Multi-Resolution Neural Field Estimation

### 2011-03-12 Multiresolution_framework/ltx/ResearchHighlights.tex
added research highlights
edit to research highlights

\textbf{Research Highlights}
\begin{itemize}
	\item We derive a model-based, data-driven estimator of continuum neural field parameters.
	\item Both macroscopic and microscopic behaviour of the system can be represented simultaneosly.
	\item We show how to infer intracortical connectivity kernel with an arbitrary shape from data.
\end{itemize}

>>>>

\textbf{Research Highlights}
\begin{itemize}
	\item We derive a multi-resolution model-based, data-driven estimator of continuum neural field parameters.
	\item With the multi-resolution approach both the macroscopic and microscopic dynamics of the system can be represented simultaneously.
	\item We show for the first time how to infer an arbitrary shaped intracortical connectivity kernel from data.
\end{itemize}
